Learning how to act: making good decisions with machine learning

### 2017-07-06 thesis/thesis_map.tex
adds to chapter 4

@@

The total reward a bandit algorithm/policy can expect to acheive depends on the distributions from which the rewards for each action are sampled. To account for this, the performance of bandit algorithms is quantified by the the difference between the reward obtained by the algorithm and the reward that would have been obtained by an oracle that selects the arm with the highest expected reward at every time step. This difference is known as the (cummulative) regret \footnote{The term regret is somewhat overloaded in the reinforcement learning liturature. There are alternative definitions that arise in the related problems of adversarial bandits and learning from expert advice. In addition, researches often refer to the expected regret as \quotes{the regret}.},
\eqn{
\label{eqn:raw_regret}
\rawregret = \sum_{t=1}^T Y_{t,i^*} - \sum_{t=1}^T Y_{t,a_t}
}

@@

\todo{consider mentioning Thompson sampling and Bayesian bandits}

@@

There are a few key hueristic principles that are used to guide the development of bandit algorithms. The first is \emph{optimism in the face of uncertainty}. Applied to stochastic bandits, the optimism in the face of uncertainty princple suggests computing a plausible upper-bound for the expected reward of each arm, and selecting the arm with the highest upper bound. The optimism principle encourages exploitation and exploration because a high upper bound on the expected reward for an action implies either the expected reward or the uncertainty about the reward for that action is high. Thus selecting it yields either a good reward or useful information.

@@

@@

Adversarial bandits are an alternate, widely studied, setting that relaxes the assumption that rewards are generated stochastically. Instead, simultaneously with the learner selecting an action $a_t$, a potentially malicious adversary selects the reward vector $\boldsymbol{Y}_t$. As in the stochastic setting, the learner then receives reward only for the selected action.

\vspace{0.5cm}
\begin{definition}[Adversarial k-armed bandit problem]
Let $\actionspace = \set{1,...k}$ be the set of available actions.  In each round $t \in 1,...,T$, 
\begin{enumerate}
\item the world (or adversary) generates, but does not reveal, a vector or rewards $\vec{Y_t}=[Y_{t,1},...,Y_{t,k}]$. 
\item the learner selects an action $a_{t} \in \set{1,...,k}$, based on the actions and rewards from previous time-steps and a (potentially stochastic) \emph{policy} $\pi$
\item the learner observes and recieves (only) the reward for the selected action $Y_{t,a_t}$ 
\end{enumerate} 
\end{definition}

@@

The pseudo-regret for adversarial bandits is defined, in the same way as for stochastic bandits, as the difference between the reward obtained by playing the single arm with the highest expected reward in every round and the expected reward obtained by the algorithm.

\eqn{
\label{eqn:pseudo_regret-adversarial}
\regret(\pi) &= \max_{i \in \set{1,...,k}}\E{\sum_{t=1}^T{Y_{t,i}}} - \E{\sum_{t=1}^T{Y_{t,a_t}}}
}

@@

\begin{figure}
  \caption{The pseudo-regret can be negative if rewards are non-stationary. This example shows the results of 1000 simulations of running the UCB-1 algorithm on a 2-armed bernoulli bandit problem where the expected rewards change linearly over time, up to a horizon $T=10,000$. Figure (a) shows the expected rewards of each arm, and the proportion of time that arm-1 is played, as a function of time. The single best-arm is arm-1 as it has the highest expected reward (averaged over $t$). An oracle that selects arm-1 in every round obtains an expected reward of $5,000$. However, despite not being designed to do so, the UCB-algorithm can adapt to the changing reward distribution to obtain costistently higher rewards. The distribution of regret over the 1000 simulations is shown in figure (b).}\label{fig:non-stationary-bandit}
    \begin{subfigure}[t]{0.49\textwidth}
	\centering   
	 \caption{Behaviour over time}\label{fig:non-stationary-bandit-time} 
         \includegraphics[scale=.5]{non-stationary-bandit-time}
\end{subfigure}
    \begin{subfigure}[t]{0.49\textwidth}
    \centering
     \caption{Cummulative regret distribution}
        \label{fig:non-stationary-bandit-regret}
        \includegraphics[scale=.5]{non-stationary-bandit-regret}
    \end{subfigure}
\end{figure}

\subsection{Contextual bandits}
Contextual bandits are a generalisation of multi-armed bandits.

\vspace{0.5cm}
\begin{definition}[Contextual bandit problem]
Let $\P{\vec{Y},\vec{X}}$ be the joint distribution over the rewards for each action and some context $\vec{x} \sim \mathcal{X}$. In each round $t \in \set{1,...T}$, 
\begin{enumerate}
\item the world stochastically generates the vector of rewards for each action and the context, $([Y_{t,1},...,Y_{t,k}],\vec{x}_t) \sim \P{\vec{Y},\vec{X}}$ and reveals $\vec{x}_t$ to the learner
\item the learner selects an action $a_{t} \in \set{1,...,k}$, based on the context as well as actions and rewards from previous time-steps.
\item the learner observes and recieves (only) the reward for the selected action $Y_{t,a_t}$ 
\end{enumerate}
\end{definition}

What are the reductions of contextual bandits to other problem (ie k armed-bandits?)

In the previous sections each decision was identical. If we were imaging treating patients, we assume that we have no additional information about each patient that is relevant to deciding how to treat them. However, in many key applications such as serving ads, etc, etc. we clearly do have additional information that we wish to take into account. In the contextual bandit setting the goal is to learn

\eq {
\P{Y|a,x}
}

As opposed to the standard bandit setting where we are attempting to estimate

\eq{
\P{Y|a}
}

The formal definition of a contextual bandit problem is

The simplest way to generalise the standard bandit algorithms to the contextual case (where the context is discrete) is to simply have a separate standard bandit instance for each possible setting of the context. Regrettably this approach scales terribly with increasing complexity of the context. \todo{quantify this}. It cannot be applied at all if the context is continuous.

The approach to solving this problem parallels those from supervised learning and continuous armed bandits. We make assumptions about the smoothness of the problem. Values of context that are similar should lead to comparable rewards for a given action.

Regret bounds \todo {insert regret bounds for contextual bandits}

It should be noted that there is an important difference between the approaches we can apply to the contextual bandit versus the supervised learning setting. As for the casual effect estimation problem, we cannot utilise cross-validation offline to select model parameters. This makes contextual bandit algorithms degrade faster than supervised learning ones as we add irrelevant variables. \todo{ask Tor if he thinks this is correct}

RUN A SIMULATION COMPARING HOW supervised learning and contextual bandits degrade as we add more features. What would be a fair comparison?

\subsubsection{Learning from logged bandit data}

@@

@@

@@

\section{Questions}
\begin{enumerate}
\item When does the expected regret make sense as the thing we actually would wish to optimise? Is optimising the expected regret any different to optimising the psuedo-regret? Who is the definition of regret down to? Does this definition of regret come from learning with expert advise?
\item Is there a reference for the doubling trick? Is it an automatic way of converting a fixed horizon algorithm to an anytime one?
\item Why is the dependence on the number of arms $K$ in the problem dependent bounds but $\sqrt{K}$ in the worst case bounds?
\item rewards in the multi-armed bandit setting can be sampled from some joint distribution?
\item Is Learning from logged feedback data just covariate shift too?
\item In contextual bandits, does it ever make sense that $Y$ causes $X$? If the reward is some function of the action taken and the context, then the full vector of counterfactual outcomes $Y$ is never instantiated. Are there any implications of this for inference?
\item Why does anything solving a regression problem work in the anti-causal direction - it would seem to break the fundamental underlying assumption of additive noise?
\item is there a benchmark library of implementations of key bandit algorithms?
\item Bubeck 2012 states that if the adversary is oblivious, the psuedo-regret coincides with the standard regret, 'which is always the ultimate quantity of interest'. Why, they are not the same for stochastic bandits are they?
\item what is the worst-case regret of UCB in an adversarial setting?
\item is there a concept of problem dependent regret for adversarial bandits? Has there been analysis of the problem dependent regret for key adversarial algorithms such as EXP-3?
\item adversarial regret bounds for Thompson sampling, UCB with random arm selection from upper-bound set?
\item do continuous armed bandits implie that there are arms with any arbitrary gap in reward (including worst case gap for that T) and thus you always end up with something like worst case regret?)
\item in what real world setting do adversarial bandits potentially make sense?
\end{enumerate}

>>>>

IF THE PROPENSITY SCORE IS THE SAME FOR ALL COVARIATES IT DOESN'T SEEM ONE MUST ADJUST.
\todo{double check}

@@

The total reward a bandit algorithm/policy can expect to acheive depends on the distributions from which the rewards for each action are sampled. To account for this, the performance of bandit algorithms is quantified by the the difference between the reward obtained by the algorithm and the reward that would have been obtained by an oracle that selects the arm with the highest expected reward at every time step. This difference is known as the (cummulative) regret \footnote{The term regret is somewhat overloaded in the reinforcement learning liturature. There are alternative definitions that arise in the related problems of adversarial bandits and learning from expert advice. In addition, researches often refer to the expected regret as \quotes{the regret}.}.
\eqn{
\label{eqn:raw_regret}
\rawregret = \sum_{t=1}^T Y_{t,i^*} - \sum_{t=1}^T Y_{t,a_t}
}

@@

@@

There are a few key principles that are used to guide the development of bandit algorithms. The simplest is to explicitly seperate exploration from exploitation and base estimation of the expected rewards of each arm only on the data generated during exploration steps. A common example in practice is unform exploration (or A/B testing) for some fixed period followed by selecting the action found to be best during the exploration phase. This results in simpler analysis, particularly if the number of exploration steps is fixed in advance, however it is sub-optimal, even if the exploration period is adaptive \citep{NIPS2016_6179}.

Another key approach is \emph{optimism in the face of uncertainty}. Applied to stochastic bandits, the optimism in the face of uncertainty princple suggests computing a plausible upper-bound for the expected reward of each arm, and selecting the arm with the highest upper bound. The optimism principle encourages exploitation and exploration because a high upper bound on the expected reward for an action implies either the expected reward or the uncertainty about the reward for that action is high. Thus selecting it yields either a good reward or useful information.

@@

Finally, there is the heuristic principle of playing each arm with probability proportional to the likelyhood that it is optimal. This approach is generally called Thompson sampling as it was the method proposed in the original bandit paper by \citet{Thompson1993}. Thompson sampling has strong empirical performance, \citep{chapelle2011empirical}. However, it is complex to analyse, \citet{kaufmann2012thompson} demonstrate that it obtains optimal problem dependent bounds, \citet{agrawal2013further} show that it obtains worst case regret of $\bigo{\sqrt{kT\log(T)}}$, equivelent to UCB.

@@

Adversarial bandits, described by \citet{Auer1995}, are an alternate, widely studied, setting that relaxes the assumption that rewards are generated stochastically. Instead, simultaneously with the learner selecting an action $a_t$, a potentially malicious adversary selects the reward vector $\boldsymbol{Y}_t$. As in the stochastic setting, the learner then receives reward only for the selected action.

\vspace{0.5cm}
\begin{definition}[Adversarial k-armed bandit problem]
\label{def:adversarial-k-armed-bandit}
Let $\actionspace = \set{1,...k}$ be the set of available actions.  In each round $t \in 1,...,T$, 
\begin{enumerate}
\item the world (or adversary) generates, but does not reveal, a vector or rewards $\vec{Y_t}=[Y_{t,1},...,Y_{t,k}]$. 
\item the learner selects an action $a_{t} \in \set{1,...,k}$, based on the actions and rewards from previous time-steps and a (potentially stochastic) \emph{policy} $\pi$
\item the learner observes and recieves (only) the reward for the selected action $Y_{t,a_t}$ 
\end{enumerate} 
\end{definition}

@@

For oblivious adversarial bandits we can define regret analagously to stochastic bandits as the difference between the reward obtained by playing the single arm with the highest reward in every round and the expected reward obtained by the algorithm \footnote{This is also refered to as the weak regret, since in the adversarial case, it can make more sense to compare against the best sequence of arms rather than the best single arm.}. We do not have to take the expectation over the first term of equation \ref{eqn:pseudo_regret-adversarial} because sequence of rewards is fixed, however the reward obtained by the algorithm is still a random variable as we are considering randomised algorithms.

\eqn{
\label{eqn:pseudo_regret-adversarial}
\regret(\pi) &= \max_{i \in \set{1,...,k}}{\sum_{t=1}^T{Y_{t,i}}} - \E{\sum_{t=1}^T{Y_{t,a_t}}}
}

@@

\begin{figure}[h]
  \caption{The pseudo-regret can be negative if rewards are non-stationary. This example shows the results of 1000 simulations of running the UCB-1 algorithm on a 2-armed bernoulli bandit problem where the expected rewards change linearly over time, up to a horizon $T=10,000$. Figure (a) shows the expected rewards of each arm, and the proportion of time that arm-1 is played, as a function of time. The single best-arm is arm-1 as it has the highest expected reward (averaged over $t$). An oracle that selects arm-1 in every round obtains an expected reward of $5,000$. However, despite not being designed to do so, the UCB-algorithm can adapt to the changing reward distribution to obtain costistently higher rewards. The distribution of regret over the 1000 simulations is shown in figure (b).}\label{fig:non-stationary-bandit}
    \begin{subfigure}[t]{0.49\textwidth}
	\centering   
	 \caption{Behaviour over time}\label{fig:non-stationary-bandit-time} 
         \includegraphics[scale=.5]{non-stationary-bandit-time}
\end{subfigure}
    \begin{subfigure}[t]{0.49\textwidth}
    \centering
     \caption{Cummulative regret distribution}
        \label{fig:non-stationary-bandit-regret}
        \includegraphics[scale=.5]{non-stationary-bandit-regret}
    \end{subfigure}
\end{figure}

\subsection{Contextual bandits}
\label{sec:contextual-bandits}

In the standard multi-armed bandit setting, each decision is identical and the goal is to learn a single best action. However, in most real life (sequential) decision making processes, which action is optimal depends on some context.  The best treatment to offer an individual patient could depend on their age, gender, disease subtype or genetics and will not always align with the treatment that is best on average (or for the majority of people).  Similarly, decisions on which ad or content to display on a webpage or which product to reccomend can be \emph{personalised} based on the previous behaviour of the user. A movie recommender system that learned a single \quotes{best} movie for everyone would not be very useful. Contextual bandits are a generalisation of multi-armed bandits that make use of this additional contextual information. The term contextual bandit was coined by \citet{Langford2008}, however close variants of the underlying problem have also been posed under the names; \quotes{associative reinforcement learning} \citep{kaelbling1994associative}, \quotes{bandits with concomitant variables}\citep{woodroofe1979one} and  \quotes{bandit problems with side information} \citep{wang2005bandit}.

\vspace{0.5cm}
\begin{definition}[Stochastic Contextual Bandit \footnote{Contextual bandits can also be defined in the adversarial setting analagously to definition \ref{def:adversarial-k-armed-bandit}}]
\label{def:contextual-bandit-problem}
Let $\P{\vec{Y},\vec{X}}$ be the joint distribution over the rewards for each action and some context $\vec{x} \sim \mathcal{X}$. In each round $t \in \set{1,...T}$, 
\begin{enumerate}
\item the world stochastically generates the vector of rewards for each action and the context, $([Y_{t,1},...,Y_{t,k}],\vec{x}_t) \sim \P{\vec{Y},\vec{X}}$ and reveals $\vec{x}_t$ to the learner
\item the learner selects an action $a_{t} \in \set{1,...,k}$, based on the context as well as actions and rewards from previous time-steps.
\item the learner observes and recieves (only) the reward for the selected action $Y_{t,a_t}$ 
\end{enumerate}
\end{definition}

Standard multi-armed bandits learn to select the action $a$ that, with high probability, maximises $\E{Y|a}$. Contextual bandits learn to select actions that maximise $\E{Y|\vec{x},a}$. The reward for contextual bandits should  be compared to an oracle that acts optimally based on the context. To achieve this, even when the context is continuous, the regret is defined with respect to a class of hypothosis that map from context to action, $h \in \mathcal{H}: \mathcal{X} \rightarrow \set{1,...,k}$. The pseudo-regret is the difference betweent the expected regret obtained by an oracle that selects actions based on the single best hypothosis or policy $h$ at each timestep, and the expected reward obtained by the algorithm.

\eqn{
\label{eqn:regret_contextual}
\regret = \max_{h \in \mathcal{H}}\E{\sum_{t=1}^T{Y_{t,h(\vec{x}_t)}}} - \E{\sum_{t=1}^T{Y_{t,a_t}}}
}

If the context is discrete, $\mathcal{X} = \set{1,...,N}$, the contextual bandit problem can be reduced to the standard multi-armed bandit problem by creating a seperate standard bandit instance for each value of the context. This approach results in a worst case regret of $\bigo{\sqrt{NkT}}$, with respect to the hypothosis class $\mathcal{H} = \mathcal{X} \times \actionspace$, consisting of all possible mappings from context to action\footnote{This follows from the fact that we have $N$ standard bandit instances, each suffering regret $\bigo{\sqrt{kT_c}}$, where $T_c$ is the number of times context $c$ occured such that $\sum_{c=1}^N T_c = T$. The regret is maximised if $T_c = T/N$ resulting in total regret $\bigo{N\sqrt{kT/N}}$.}. This is optimal with respect to this class of hypothosis. However, as this reduction treats the problem of learning the correct action for each context completely independently, it cannot leverage any stucture in the in the relationships between different contexts and actions. As in the supervisied learning setting, the existance of some form of low-dimensional structure is key to learning in realistic problems, where the context is continous or high-dimensional \footnote{Even if the context is genuintly discrete, $N$ grows exponentially with the number of variables. For example, with $n$ binary variables, $N = 2^n$}. We expect some form of smoothness; values of context that are similar should lead to comparable rewards for a given action. We need algorithms that can leverage such assumptions.

An alternate reduction to the standard bandit problem, which allows us to constrain the hypothosis space to explore, is to treat each hypothosis $h$ as a bandit arm \citep{Langford2008}. At each time-step, we select $h \in \mathcal{H}$ based on the rewards previously observed for each hypthosis, take action $h(\vec{x})$ and observe the associated reward. Although this approach removes the explicit dependence on the size of the context, the regret  grows linearly with the size of the hypothosis class considered, limiting our ability to learn any complex mappings from context to actions. The key problem with this approach is each sample is used to update our knoweledge about only one hypothosis, as opposed to the supervised learning setting, where each data point is (implicitly) used to compute the loss for every hypothosis simultaneously.

Suppose that, at each timestep $t$, after selecting an action, the learner recieved the reward for chosen action but observed the full vector of rewards $[Y_{t,1},...,Y_{t,k}]$. This is known as the full information setting. In this case, the learner can simulate running each hypothosis over the history to compute the reward it would have obtained and use the hypothosis with the best empirical reward to select the next action. This is the \emph{follow the leader} algorithm, which obtains optimal regret $\bigo{\sqrt{T log(\card{\mathcal{H}})}}$ for the full-information problem \citep{cesa2006prediction}. Unfortunately, in the contexual bandit problem, the (counterfactual) rewards associated with alternate action choices are not observed. As in causal effect estimation, we can view this as a missing data problem. However, the data is missing not at random because which component of the reward is observed depends on the action selected which in turn is a function of the previous history of actions and rewards.

The Epoch-greedy algorithm, \citep{Langford2008}, addresses these issues by transforming the contextual bandit problem into a data missing at random problem by explicitly seperating exploration from exploitation. Epoch-greedy is an explore-explot algorithm. It selects actions uniformly at random during an exploration phase and leverages this data to estimate the value of each hypothosis, using inverse propensity weighted estimators to \quotes{fill in} the missing data. The hypothosis with the highest empirical reward is then used to select actions for the remaining timesteps. The epsilon-greedy algorithm obtains worst case regret $\bigo{T^{\frac{2}{3}}(k \log{\card{\mathcal{H}}})^{\frac{1}{3}}}$, which has sub-optimal dependence on the horizon $T$.

The Exp-4 algorithm, developed in the context of learning from expert advice (each $h \in \mathcal{H}$ can be viewed as an expert who recommends which action to take), achieves optimal worst case regret of $\bigo{\sqrt{kT log(\card{\mathcal{H}})}}$ in both the stochastic and adversarial settings \citep{Auer2002a}. However, it involves maintaining a list of weights for each hypothosis $h$ resulting in time and memory requirements that grow linearly with the size of the hypothosis space and, unlike the epoch-greedy algorithm, it cannot be generalised to infinite dimensional hypothosis spaces in a straighforward way. The ILOVECONBANDITS algorithm combines the best of both worlds to obtain a computationally efficient algorithm with (almost) optimal regret \citep{Agarwal2014}

Both Epoch-greedy and ILOVECONBANDITS involve solving problems of the form,

\eqn{
\argmax_{h \in \mathcal{H}} \sum_{t=1}^\tau Y_t \ind{h(\vec{x}_t) = a_t}
}

This expression equates to identifying the best emprical policy based on previous data. The algorithms assume the existance of an oracle that can solve this problem and report complexity in terms of the number of calls required to the oracle. The computational tractability of these algorithms on large (or infinite) hypothosis spaces stems from the fact that this problem (also known as the argmax-oracle), can be reduced to solving a cost sensitive classiciation problem \citep{Dudik2011a}.

Finally, if we have a parametric model for the relationship between context, action and reward that allows (efficient) computation of the posterior or confidence bounds on the reward for each arm given context, we can develop generalized versions of the UCB or Thompson sampling algorithms. For linear pay off models, both approaches yield algorithms with strong regret guarantees, Lin-UCB \citep{li2010contextual} and generalised thompson sampling for linear pay-offs \citep{Agrawal2013}.

It is worth noting that definition \ref{def:contextual-bandit-problem} does not make any assumptions about the \emph{causal} relationship between the context $\vec{X}$ and the reward $\vec{Y}$, see figure \ref{fig:contextual-bandit-causal-graph}. \citet{Bareinboim2015} demonstrate that policies that incorporate observations of the action an agent would have taken were their action not set by the bandit policy can acheive lower regret than those that ignore this information. This is an example of the case represented in figure \ref{fig:context-graph-confounded}. However, the context should be relevent, such that $\P{\vec{Y}|\vec{X}} \neq \P{\vec{Y}}$, otherwise including it is the equivelent to adding irrelevent featurs to a supervised learning problem.

\begin{figure}[h]
\centering
\caption{Several potential causal graphical models for the contextual bandit problem (if actions are selected at random). $\vec{X}$ and $\vec{Y}$ represent the context and reward vectors respectively, and $Y = \vec{Y}_a$ is the reward recieved by the learner, which is a deterministic function of $\vec{Y}$ and $a$. Regardless of the causal structure, observing the context $\vec{X}$ provides information about the vector of rewards $\vec{Y}$. To represent a realistic (contextual) bandit problem, where actions are not selected at random, we would need to \quotes{unroll} the graphs, such that there was a copy for each time-step $t$ and allow the action $a_t$ to depend on the context $\vec{X}_t$ and the previous observations $(\vec{X},a,Y)_1^{t-1}$. }
\label{fig:contextual-bandit-causal-graph}
\begin{subfigure}[t]{0.29\textwidth}
\centering
\caption{$\vec{X}$ causes $\vec{Y}$}
\label{fig:context-graph-causal}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1cm,
  thick,main node/.style={observed},lt/.style={latent}]
 %nodes
\node[lt](1){$\vec{Y}$};
\node[main node, below=of 1](2){$Y$};
\node[main node, above right=of 2](3){$a$};
\node[main node, left=of 1](4){$\vec{X}$};
 \path[every node/.style={font=\sffamily\small}]
   (4) edge (1)
   (3) edge (2)
   (1) edge (2);
\end{tikzpicture} 
\end{subfigure}
\begin{subfigure}[t]{0.29\textwidth}
\centering
\caption{$\vec{Y}$ causes $\vec{X}$}
\label{fig:context-graph-anti-causal}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1cm,
  thick,main node/.style={observed},lt/.style={latent}]
 %nodes
\node[lt](1){$\vec{Y}$};
\node[main node, below=of 1](2){$Y$};
\node[main node, above right=of 2](3){$a$};
\node[main node, left=of 1](4){$\vec{X}$};
 \path[every node/.style={font=\sffamily\small}]
   (1) edge (4)
   (3) edge (2)
   (1) edge (2);
\end{tikzpicture} 
\end{subfigure}
\begin{subfigure}[t]{0.29\textwidth}
\centering
\caption{$\vec{X}$ and $\vec{Y}$ are counfounded}
\label{fig:context-graph-confounded}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1cm,
  thick,main node/.style={observed},lt/.style={latent}]
 %nodes
\node[lt](1){$\vec{Y}$};
\node[main node, below=of 1](2){$Y$};
\node[main node, above right=of 2](3){$a$};
\node[main node, left=of 1](4){$\vec{X}$};
\node[lt, below=of 4](5){$U$};
 \path[every node/.style={font=\sffamily\small}]
   (3) edge (2)
   (1) edge (2)
   (5) edge (4) edge (1);
\end{tikzpicture}
\end{subfigure}
\end{figure}

\subsubsection{Learning from logged bandit data}
Another topic of interest within the contextual bandit community that is deeply related to causal effect estimation from observational data is learning from logged bandit feedback data \citep{}.

If no assumptions are made about the behaviour of the hypothosis that generated the data.... does it reduce to causal effect estimation?

However, in the applications considered in these setting such as ad serving, the details of the hypothosis generating the data are often known.

@@

\subsubsection{Limitations of bandit problems}
\begin{itemize}
\item Reward needs to be observed immediately after action is taken (or at least before the next action must be selected).
\item State assumed not to change

Reward known immediately. Action chosen for one individual does not effect reward for the next (SUTVA).

@@

causal bandits capture a very natural form of structure that can arise between different arms.

@@

\section{Questions}
\begin{enumerate}
\item In the $\epsilon$-greedy approach, does one compute best action based only on exploration steps?
\item Why does the naive reduction appear to get sub-optimal regret?
\item When does the expected regret make sense as the thing we actually would wish to optimise? Is optimising the expected regret any different to optimising the psuedo-regret? Who is the definition of regret down to? Does this definition of regret come from learning with expert advise?
\item Is there a reference for the doubling trick? Is it an automatic way of converting a fixed horizon algorithm to an anytime one?
\item Is Learning from logged feedback data just covariate shift too?
\item In contextual bandits, does it ever make sense that $Y$ causes $X$? If the reward is some function of the action taken and the context, then the full vector of counterfactual outcomes $Y$ is never instantiated. Are there any implications of this for inference?
\item Why does anything solving a regression problem work in the anti-causal direction - it would seem to break the fundamental underlying assumption of additive noise?
\item is there a benchmark library of implementations of key bandit algorithms?
\item Bubeck 2012 states that if the adversary is oblivious, the psuedo-regret coincides with the standard regret, 'which is always the ultimate quantity of interest'. Why, they are not the same for stochastic bandits are they?
\item what is the worst-case regret of UCB in an adversarial setting?
\item is there a concept of problem dependent regret for adversarial bandits? Has there been analysis of the problem dependent regret for key adversarial algorithms such as EXP-3?
\item adversarial regret bounds for Thompson sampling, UCB with random arm selection from upper-bound set?
\item do continuous armed bandits implie that there are arms with any arbitrary gap in reward (including worst case gap for that T) and thus you always end up with something like worst case regret?)
\item in what real world setting do adversarial bandits potentially make sense?
\item Does supervised learning really 'reveal the value of every action'.
\end{enumerate}
